The title

### 2019-06-18 analysis/paper/paper.Rnw
commented out line for todonotes latex package
fixed Makefile & paper.Rnw

\documentclass[oneside]{book}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
%\linenumbers

@@

\doublespacing
\begin{titlepage}\thispagestyle{empty}
\tableofcontents
%\listoffigures
%\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\chapter{Introduction}

@@

\begin{figure}
  \centering
  \includegraphics[width = 0.7\textwidth]{../QTLfigs/Figs/central_dogma.pdf}
  \caption{Biological information is encoded in DNA. This information is passed, via transcription, to sequence-specific RNA molecules. The process of translation transmits the information to sequence-specific proteins.}\label{fig:dogma}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width = 0.7\textwidth]{../QTLfigs/Figs/central_dogma-Dhtkd1.pdf}
  \caption{A DNA variant in the \emph{Dhtkd1} gene affects \emph{Dhtkd1} transcript abundances which, in turn, affect DHTKD1 protein concentrations.}\label{fig:Dhtkd1}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/confounding.pdf}
\caption{Example causal diagram showing relationships between random variables in an expression QTL study.}\label{fig:confounding}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.7\textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/lod-diff-prop-v-lrt.eps}
    \caption[LOD difference proportion vs. pleiotropy test statistic]{LOD difference proportion against pleiotropy vs. separate QTL test statistics for 1911 pairs of traits.
    Each point represents a single pair. Pairs that involve local expression trait \emph{Hnf4a} are colored red, while all others are colored blue.
    Note the high concentration of red points in the upper left quadrant of the figure.
    These points, with low values of the pleiotropy vs. separate QTL test statistic and
    high values of LOD difference proportion, are consistent with \emph{Hnf4a} transcript
    levels mediating the effect of \emph{Hnf4a} genetic variants affecting nonlocal
    transcript abundances.}
    \label{fig:lod-diff-prop-v-lrt-all}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width = \textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/Hnf4a-lod-diff-prop-v-lrt.eps}
    \caption[LOD difference proportion vs. pleiotropy test statistic.]{Scatter plot of LOD difference proportion against pleiotropy vs.
    separate QTL test statistic for 147 pairs of traits.
    Each pair includes \emph{Hnf4a} and one of the nonlocal gene expression traits that map to the Chromosome 2 hotspot.}
    \label{fig:hnf4a}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width = 0.8\textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/12local-facet_grid-no-strip.eps}
    \caption[LOD difference proportion vs. pleiotropy test statistic from the per-local gene perspective.]{Scatter plots of LOD difference proportion against pleiotropy vs. separate QTL
    test statistic with 147 pairs of traits per panel.
    Each panel includes a local gene expression trait
    (per the label in the upper right quadrant) and one of the 147 nonlocal gene
    expression traits that map to the Chromosome 2 hotspot.}
    \label{fig:nothnf4a-12}
\end{figure}

@@

\begin{figure}
    \centering
    \caption{Scatter plots for four nonlocal expression traits. Each plot features 13
    points, one for each local gene expression trait. The vertical axis denotes LOD
    difference proportion values, while the horizontal axis corresponds to pleiotropy test
    statistics. Red points represent the pairing with local gene expression trait
    \emph{Hnf4a}. Blue points represent the other 12 local gene expression traits.}
    \begin{subfigure}[t]{.45\textwidth}
        \includegraphics[width = \textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/nonlocal-scatter_97.eps}
        \caption[\emph{Hnf4a} transcript levels mediate \emph{Abcb4} transcript levels.]{\emph{Hnf4a} transcript levels mediate \emph{Abcb4} transcript levels. The high LOD difference proportion and the very small pleiotropy test statistic together provide evidence that \emph{Hnf4a} mediates \emph{Abcb4} transcript levels.}
    \end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}[t]{.45\textwidth}
        \includegraphics[width = \textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/nonlocal-scatter_105.eps}
        \caption[\emph{Hnf4a} transcript levels mediate \emph{Smim5} transcript levels.]{\emph{Hnf4a} transcript levels mediate \emph{Smim5} transcript levels. The high LOD difference proportion and the very small pleiotropy test statistic together provide evidence that \emph{Hnf4a} mediates \emph{Smim5} transcript levels.}
    \end{subfigure}
    \begin{subfigure}[t]{.45\textwidth}
        \includegraphics[width = \textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/nonlocal-scatter_64.eps}
        \caption[\emph{Tmprss4} transcript levels are not mediated by any of the 13 local gene expression traits.]{\emph{Tmprss4} transcript levels are not mediated by any of the 13 local gene expression traits. However, several local gene expression traits arise from separate QTL, as evidenced by their large (greater than 5) values of the pleiotropy test statistic.}
    \end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}[t]{.45\textwidth}
        \includegraphics[width = \textwidth]{../keller2018-chr2-hotspot-chtc/Rmd/nonlocal-scatter_141.eps}
        \caption[\emph{Gm3095} transcript levels are not mediated by any of the 13 local genes.]{\emph{Gm3095} transcript levels are not mediated by any of the 13 local genes. The tests of pleiotropy demonstrate evidence of separate QTL for some local expression traits when paired with \emph{Gm3095}.}
    \end{subfigure}
    \label{fig:4nonlocal}
\end{figure}

>>>>

\documentclass[oneside]{book}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
%\linenumbers

@@

\doublespacing
\tableofcontents
%\listoffigures
%\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\chapter{Introduction}

@@

@@

@@

@@

@@
